RandomForest

### 2021-12-05 randomforest.Rmd
Representative Tree plot

@@

@@

>>>>

options(repos='http://cran.rstudio.org')
have.packages <- installed.packages()
cran.packages <- c('devtools','plotrix','randomForest','tree')
to.install <- setdiff(cran.packages, have.packages[,1])
if(length(to.install)>0) install.packages(to.install)

library(devtools)
if(!('reprtree' %in% installed.packages())){
  install_github('araastat/reprtree')
}
for(p in c(cran.packages, 'reprtree')) eval(substitute(library(pkg), list(pkg=p)))

@@

```{r}
library(reprtree)
```

@@

```{r}
reprtree:::plot.getTree(rf_fit)
```

https://stats.stackexchange.com/questions/41443/how-to-actually-plot-a-sample-tree-from-randomforestgettree

Identifying representative trees from ensembles
Banerjee, Mousumi ; Ding, Ying ; Noone, Anne-Michelle
Chichester, UK: John Wiley & Sons, Ltd
Statistics in medicine, 2012-07-10, Vol.31 (15), p.1601-1616
